Red Oak: Something Something Algorithmic Policy

### 2015-05-05 draft.tex
..

@@

\begin{figure}[ht]
\begin{lstlisting}
f(pkt):
  if Oak.in_range(pkt, src, 0, 10) then
     if Oak.in_range pkt dst  [(0,10)] then
        Oak.deliver
     else 
        Oak.add pkt (Oak.IpDst, Oak.IpSrc) ``conn'';
        Oak.deliver
  else if Oak.in_rel pkt (Oak.IpSrc,Oak.IpDst) ``conn'' then
         Oak.deliver
       else
         RO.drop
       end
  end                
  \end{lstlisting}

>>>>

\begin{abstract} ...
\end{abstract}

@@

\begin{figure}[ht]
\begin{lstlisting}
f(pkt):
  if in_range(pkt, src, 0, 10) then
     if in_range pkt dst  [(0,10)] then
        deliver
     else 
        add pkt (IpDst, IpSrc) ``conn'';
        deliver
  else if in_rel pkt (IpSrc,IpDst) ``conn'' then
         deliver
       else
         RO.drop
       end
  end                
  \end{lstlisting}
